\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

%% Pointer to 'default' preamble, other reusable files
\input{../../thad_preamble.tex}
\input{../../thad_cmds.tex}

%% Header
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Talking Points \\ Week of September 29th, 2019}
\lhead{Research \\ }

%\usepackage{graphicx}
%\graphicspath{ {figures/} }
%\newcommand{\caseName}{ }

\begin{document}
\begin{multicols}{2}
\raggedright
	\paragraph{Recent Progress:}
	\begin{enumerate}
		\item Results from turbine type code.
		\item Re-test of WECC flatlines 
			\subitem 18,16 still seem to not work
			\subitem redownloaded, and reinstalled
			\subitem made with 21.0\_02

		\item Generic generator created
		\item Generic governor work started
			\subitem got gas params from Dan
			\subitem \verb|lcfb1| = load controller.
			
		\item Update of Tgov1 to account for area gov deadband.

	%	\item More \verb|matplotlib| plot functions created.

		\item GitHub updated:\\
		\verb|https://github.com/thadhaines/|
		
	\end{enumerate}
\paragraph{Current Tasks:}
	\begin{enumerate}
	
		\item Generic Governor Coding
		\item Don't forget to Refine BA ACE actions.
		\item Update Code flowchart% to aid in further development.
		\item Thesis Outline and Introduction 
		\item Paper outline?
		%\item Keep Goals and Requests in mind.
		
		%\subitem A FlowtabrDAO exists that can find flow between busses. A way to initialize bus connections between areas has yet to be devised.

	\end{enumerate}

	\paragraph{Current Questions:}
	\begin{enumerate}
	\item Realistic AGC results?
	\item Typical deadbands of AGC? 
	\item Paper outline?
	\item What to do with wind generators and governors? (no H, no R?)
	\item Types of generic governors to create? Steam, Hydro, Gas ...
	\item Turbine type to governor type check
	
\vfill\null
\columnbreak

\paragraph{Future Tasks:} %(Little to No Progress since last time / Things coming down the pipe)
	\begin{enumerate}
		
		\item Add import mirror / bypass mirror init sequence option to prevent repeated mirror creations.

		\item Bring wind into simulation \\ (ramp ungoverned generators?)

		\item Find best/correct way to trip gens in PSLF from python.

		\item Investigate line current data.
		
	\end{enumerate}
\paragraph{Future Work: (not by me)}
\begin{itemize}
\item Account for different types of loads. (exponential load model) % read from dyd
\item Work to incorporate Matt's \emph{Suggested Use Cases} into simulation.
		\begin{itemize}
		\item Add Shunt Group Agent
		\item Work to Define Definite Time Controller user input
		\end{itemize} 


		\item Investigate ULTC action.

		\item Create an agent for every object: \\ ULTC, SVD, Transformer, \ldots

		\item Get away from reliance on GE
		
\end{itemize}

\paragraph{Matt Requests:}
\begin{enumerate}
		\item Enable multiple dyd files to overwrite / replace previously defined agents/parameters
		\item Allow for variable time steps.
\end{enumerate}

	\end{enumerate}



\vfill\null

\end{multicols}
\pagebreak


%\paragraph{'Soft Goals':}
%	\begin{enumerate}
%	\item Write Thesis 2020
%	\end{enumerate}
		

\begin{comment}

\end{comment}

\end{document}