\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

\usepackage{geometry}
\geometry{
	letterpaper, 
	portrait, 
	top=.75in,
	left=.8in,
	right=.75in,
	bottom=.5in		} 	% Page Margins
	
%% additional packages for nice things
\usepackage{amsmath} 	% for most math
\usepackage{commath} 	% for abs
\usepackage{lastpage}	% for page count
\usepackage{amssymb} 	% for therefore
\usepackage{graphicx} 	% for image handling
\usepackage{wrapfig} 	% wrap figures
\usepackage[none]{hyphenat} % for no hyphenations
\usepackage{array} 		% for >{} column characterisctis
\usepackage{physics} 	% for easier derivative \dv....
\usepackage{tikz} 		% for graphic@!
\usepackage{circuitikz} % for circuits!
\usetikzlibrary{arrows.meta} % for loads
\usepackage[thicklines]{cancel}	% for cancels
\usepackage{xcolor}		% for color cancels
\usepackage[per-mode=fraction]{siunitx} % for si units and num
\usepackage{fancyhdr} 	% for header
\usepackage{comment}	% for ability to comment out large sections
\usepackage{multicol}	% for multiple columns using multicols
\usepackage[framed,numbered]{matlab-prettifier} % matlab sytle listing
\usepackage{marvosym} 	% for boltsymbol lightning
\usepackage{pdflscape} 	% for various landscape pages in portrait docs.
%\usepackage{float}
\usepackage{fancyvrb}	% for Verbatim (a tab respecting verbatim)
\usepackage{enumitem}	% for [resume] functionality of enumerate
\usepackage{spreadtab} 	% for using formulas in tables}
\usepackage{numprint}	% for number format in spread tab
% for row colors in tables....
\usepackage{color, colortbl}
\definecolor{G1}{gray}{0.9}
\definecolor{G2}{rgb}{1,0.88,1}%{gray}{0.6}
\definecolor{G3}{rgb}{0.88,1,1}

% For table formatting
\usepackage{booktabs}
\renewcommand{\arraystretch}{1.2}
\usepackage{floatrow}
\floatsetup[table]{capposition=top} % put table captions on top of tables

% Caption formating footnotesize ~ 10 pt in a 12 pt document
\usepackage[font={small}]{caption}

%% package config 
\sisetup{output-exponent-marker=\ensuremath{\mathrm{E}}} % for engineer E
\renewcommand{\CancelColor}{\color{red}}	% for color cancels
\lstset{aboveskip=2pt,belowskip=2pt} % for more compact table
%\arraycolsep=1.4pt\def
\setlength{\parindent}{0cm} % Remove indentation from paragraphs
\setlength{\columnsep}{0.5cm}
\lstset{
	style      = Matlab-editor,
	basicstyle = \ttfamily\footnotesize, % if you want to use Courier - not really used?
}
\renewcommand*{\pd}[3][]{\ensuremath{\dfrac{\partial^{#1} #2}{\partial #3}}} % for larger pd fracs
\renewcommand{\real}[1]{\mathbb{R}\left\{ #1 \right\}}	% for REAL symbol
\newcommand{\imag}[1]{\mathbb{I}\left\{ #1 \right\}}	% for IMAG symbol
\definecolor{m}{rgb}{1,0,1}	% for MATLAB matching magenta
	
%% custom macros
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}} % for simple \numberthis command

\newcommand{\equal}{=} % so circuitikz can have an = in the labels
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%% Header
\pagestyle{fancy} % for header stuffs
\fancyhf{}
\rhead{Thad Haines \\ Page \thepage\ of \pageref{LastPage}}
\chead{Required Actions for New Agent Incorporation  \\ }
\lhead{Research \\ }
% spacing
\headheight 29 pt
\headsep 6 pt

\begin{document}
\paragraph{Class Methods:} Each agent class is required to have the following methods so that it is incorporated into the simulation correctly.
\begin{enumerate}
\item \textbf{init Function:} Collects all parameters used for identification and simulation. Creates a \verb|cv| dictionary of values that can be used in later automation.
\item \textbf{getPref:} Uses information gathered from \verb|init| process to return the agents PSLF reference object.
\item \textbf{getPvals:} Sets \verb|cv| values to that of the PSLF object.
\item \textbf{setPvals:} Sets PSLF values to that of the python mirror
\item \textbf{makeAMQPmsg:} Creates a dictionary message that contains required information for find functions and any values that should be updated.
\item \textbf{recAMQPmsg:} Set the received AMQP message values to current agent values.
\begin{enumerate}
\item AMQP functions require the agentUpdate AMQP function to be altered.
\item A suitable find function is also required
\item The find function should use a search dictionary to optimize searching.
\end{enumerate}
\item \textbf{initRunningVals:} Create lists of appropriate length for any running values to be recorded during simulation.
\item \textbf{logStep:} Sets current values to corresponding running value in log lists.
\begin{enumerate}
\item Agent collection must be added to the log collection so that its logStep method is called every step.
\end{enumerate}
\item \textbf{popUnsetData:} Removes any unset data in the case of a system crash
\item \textbf{getDataDict:} Returns a dictionary with running values. Used for .MAT export.
\end{enumerate} 
\paragraph{runSim\_IPY:} Agent collection should be added to the \verb|agentPSLFupdate| list if it interacts with PSLF (changes a PSLF value).


\end{document}